Statistical Inference for inter-arrival times of extreme events in bursty time series

### 2020-09-07 article_springer/article_springer.Rmd
Changed abstract, so that it is only one paragraph (see editors comment)
Added quotation mark on top of p.5. ( see Ref 2)

abstract: |
  In many complex systems studied in statistical physics, 
  inter-arrival times between events such as solar flares, trades and 
  neuron voltages follow a heavy-tailed distribution. The set of event times is fractal-like, 
  being dense in some time windows and empty in others, a phenomenon which has been dubbed 
  "bursty".

  A new model for the _inter-exceedance times_ of events 
  above high thresholds is proposed. For high thresholds and 
  infinite-mean waiting times, it is shown that the times between threshold 
  crossings are Mittag-Leffler distributed, and thus form a "fractional 
  Poisson Process" which generalizes the standard Poisson Process of threshold
  exceedances.
  Graphical means of estimating model parameters and assessing 
  model fit are provided. 
  The inference method is
  applied to an empirical bursty time series, and it is shown how the memory of the
  Mittag-Leffler distribution affects prediction of the time until
  the next extreme event."

@@

In this section we state and prove the key theorem, which is founded on the concept of regular variation. A Borel-measurable function $f:\mathbb (0,\infty) \to (0,\infty)$ is said be "regularly varying at $\infty$ with parameter (or "index") $\rho$ if

>>>>

abstract: |
  In many complex systems studied in statistical physics, 
  inter-arrival times between events such as solar flares, trades and 
  neuron voltages follow a heavy-tailed distribution. The set of event times is fractal-like, 
  being dense in some time windows and empty in others, a phenomenon which has been dubbed 
  "bursty". A new model for the _inter-exceedance times_ of such events 
  above high thresholds is proposed. For high thresholds and 
  infinite-mean waiting times, it is shown that the times between threshold 
  crossings are Mittag-Leffler distributed, and thus form a "fractional 
  Poisson Process" which generalizes the standard Poisson Process of threshold
  exceedances.
  Graphical means of estimating model parameters and assessing 
  model fit are provided. 
  The inference method is
  applied to an empirical bursty time series, and it is shown how the memory of the
  Mittag-Leffler distribution affects prediction of the time until
  the next extreme event."

@@

In this section we state and prove the key theorem, which is founded on the concept of regular variation. A Borel-measurable function $f:\mathbb (0,\infty) \to (0,\infty)$ is said be "regularly varying" at $\infty$ with parameter (or "index") $\rho$ if
